---
title: "API Practice - Ventura River Time series"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---
# `dataRetrieval' 
The dataRetrieval package was created to simplify the process of loading hydrologic data into the R environment. It is designed to retrieve the major data types of U.S. Geological Survey (USGS) hydrologic data that are available on the Web. 


# Instructions 
- Using `dataRetrieval` get the discharge (ft³/s) time-series for the Ventura River (site 11118500) during the recent Hilary tropical storm from 2023-08-19 to 2023-08-22


```{r}
library(tidyverse)
library(dataRetrieval)
```


```{r}
# Set parameters for the query 
siteNumber <- "11118500"
parameterCd <- "00060" # Discharge
startDate <- "2023-08-19"
endDate <- "2023-08-22"
```


```{r}
# query the data 
discharge <- readNWISdv(siteNumber, parameterCd, startDate, endDate)

# USGS daily value qualification codes are often “A” (approved for publication) or “P” (provisional data subject to revision).
```


- Plot the time-series using ggplot2
```{r}
# Date and X_00060_00003
# Discharge [ft3/s]

ggplot(data = discharge, aes(x = discharge$Date, y = discharge$X_00060_00003)) +
  geom_line() + 
  geom_point() +
  labs(x = "Date",
       y = "Discharge [ft3/s]")
```


- What was the maximum discharge during this period of time?
```{r}
# need to query the data from that time period, this time finding maximum 
# stat code 00001	Maximum

siteNumber <- "11118500"
parameterCd <- "00060" # Discharge
statCd <- "00001" # maximum
startDate <- "2023-08-19"
endDate <- "2023-08-22"

```

```{r}
maxdischarge <- readNWISdv(siteNumber, parameterCd,
  startDate, endDate,
  statCd = statCd
)
# no data available 
# just to check i also included "00003" (mean) in the statCd and it did give that info. Just the max doesn't seem to work / have that avaliable data 
```


